Mental Health Screening in CF

### 2023-01-04 Emily Muther/mental_health_screening.qmd
Update mental_health_screening.qmd
tidyverse formatting

---
title: "Mental Health Screening in CF"
author: "Tim Vigers"
date: "`r format(Sys.time(), '%d %B %Y')`"
format:
  html:
    toc: true
    toc-depth: 5
    toc-float: true
    code-fold: true
    self-contained: true
    fig-cap-location: top
    page-layout: full
editor: visual
---

```{r}
#| include: false
library(tidyverse)
library(lubridate)
```

```{r}
# Data import
cf_gad = read.csv("Z:/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Emily Muther/Mental Health Screening/Data_Raw/GAD-7_General_Anxiety_Disorder_Full_Data_data_11-15-22.csv",na.strings = "")
cf_phq = read.csv("Z:/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Emily Muther/Mental Health Screening/Data_Raw/PHQ-9_Full_Data_data_11-11-22.csv",na.strings = "")
cf_psc = read.csv("Z:/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Emily Muther/Mental Health Screening/Data_Raw/PSC_Full_Data_data_11-11-22.csv",na.strings = "")
# Select and merge
cf_gad = cf_gad %>% select(PAT_MRN_ID,CONTACT_DATE,GAD.7.Total.Score,GAD.7.Totals) %>% drop_na()
cf_phq = cf_phq %>% 
  select(PAT_MRN_ID,CONTACT_DATE,PHQ.9.Total.Score..calculated.,PHQ.9.Totals) %>% drop_na()
cf_psc = cf_psc %>% select(PAT_MRN_ID,CONTACT_DATE,Score,PSC.Totals) %>% drop_na()
df = cf_gad %>% 
  full_join(cf_phq,by = c("PAT_MRN_ID", "CONTACT_DATE")) %>%
  full_join(cf_psc,by = c("PAT_MRN_ID", "CONTACT_DATE"))
# Get age
pa = read.csv("Z:/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Emily Muther/Mental Health Screening/Data_Raw/CF_Psychosocial_Assessment_Full_Data_data_11-15-22.csv",na.strings = "")
pa = pa %>% select(PAT_MRN_ID,CONTACT_DATE,AGE_AT_CONTACT_IN_YEARS)
# Rename columns, get distinct rows
df = left_join(df,pa,by = c("PAT_MRN_ID", "CONTACT_DATE")) %>% 
  select(PAT_MRN_ID,CONTACT_DATE,AGE_AT_CONTACT_IN_YEARS,everything()) %>%
  rename(id = PAT_MRN_ID,date = CONTACT_DATE,age=AGE_AT_CONTACT_IN_YEARS,
         `GAD-7 Total` = GAD.7.Total.Score,
         `GAD-7 Category`=GAD.7.Totals,
         `PHQ-9 Total`=PHQ.9.Total.Score..calculated.,
         `PHQ-9 Category`=PHQ.9.Totals,
         `PSC-17 Total`=Score,
         `PSC-17 Category`=PSC.Totals) %>%
  distinct()
df$date = parse_date(df$date,approx = F)
df = df %>% arrange(id,date)
```

# Table

```{r}
#| label: tbl-planets
#| tbl-cap: Planets

```

# Figure

```{r}
#| label: fig-planets
#| fig-cap: Planets

```

>>>>

---
title: "Mental Health Screening in CF"
author: "Tim Vigers"
date: "`r format(Sys.time(), '%d %B %Y')`"
format:
  html:
    toc: true
    toc-depth: 5
    toc-float: true
    code-fold: true
    self-contained: true
    fig-cap-location: top
    page-layout: full
editor: source
---

```{r}
#| include: false
library(lubridate)
library(tidyverse)
```

```{r}
# Data import
cf_gad <- read.csv("/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Emily Muther/Mental Health Screening/Data_Raw/GAD-7_General_Anxiety_Disorder_Full_Data_data_11-15-22.csv", na.strings = "")
cf_phq <- read.csv("/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Emily Muther/Mental Health Screening/Data_Raw/PHQ-9_Full_Data_data_11-11-22.csv", na.strings = "")
cf_psc <- read.csv("/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Emily Muther/Mental Health Screening/Data_Raw/PSC_Full_Data_data_11-11-22.csv", na.strings = "")
# Select and merge
cf_gad <- cf_gad %>%
  select(PAT_MRN_ID, CONTACT_DATE, GAD.7.Total.Score, GAD.7.Totals) %>%
  drop_na()
cf_phq <- cf_phq %>%
  select(PAT_MRN_ID, CONTACT_DATE, PHQ.9.Total.Score..calculated., PHQ.9.Totals) %>%
  drop_na()
cf_psc <- cf_psc %>%
  select(PAT_MRN_ID, CONTACT_DATE, Score, PSC.Totals) %>%
  drop_na()
df <- cf_gad %>%
  full_join(cf_phq, by = c("PAT_MRN_ID", "CONTACT_DATE")) %>%
  full_join(cf_psc, by = c("PAT_MRN_ID", "CONTACT_DATE"))
# Get age
pa <- read.csv("/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Emily Muther/Mental Health Screening/Data_Raw/CF_Psychosocial_Assessment_Full_Data_data_11-15-22.csv", na.strings = "")
pa <- pa %>% select(PAT_MRN_ID, CONTACT_DATE, AGE_AT_CONTACT_IN_YEARS)
# Rename columns, get distinct rows
df <- left_join(df, pa, by = c("PAT_MRN_ID", "CONTACT_DATE")) %>%
  select(PAT_MRN_ID, CONTACT_DATE, AGE_AT_CONTACT_IN_YEARS, everything()) %>%
  rename(
    id = PAT_MRN_ID, date = CONTACT_DATE, age = AGE_AT_CONTACT_IN_YEARS,
    `GAD-7 Total` = GAD.7.Total.Score,
    `GAD-7 Category` = GAD.7.Totals,
    `PHQ-9 Total` = PHQ.9.Total.Score..calculated.,
    `PHQ-9 Category` = PHQ.9.Totals,
    `PSC-17 Total` = Score,
    `PSC-17 Category` = PSC.Totals
  ) %>%
  distinct()
# Format columns and sort
df$date <- mdy(df$date)
df <- df %>%
  mutate(across(contains("Category"), factor)) %>%
  arrange(id, date)
# Write cleaned data
write.csv(df, file = "/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Emily Muther/Mental Health Screening/Data_Cleaned/cf_mental_health_screening.csv")
```

```{r}
skimr::skim(df)
```
